

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Basic stats

```{r}
rivit <- read.csv2("Tilastot.csv", stringsAsFactors = FALSE)
nrow(rivit)

table(do.call(c,rivit))
```


# Cumulative proportions

Cumulative proportions of 1, X and 2 outcomes

```{r}
source("outcome_proportions.R")
```

# Frequencies of 0, 1, .., 13 homewins

According to the data, the proportion of hometeam wins ("1") is 0.45 and the proportions of draws and losses are almost identical.  

Here we compute the expected frequencies of rows with 0, 1, ..., 13 homewins and then compare to the observed frequencies.  

Expected homewins assumption: the probability of a homewin is 0.45 for each match.

```{r}
source("homewins.R")
```

# P(three or more identical rows)

The data included three of the same rows, which should be somewhat unlikely because there are 

```{r}
3^13
```

unique possible rows.

The probability of observing three or more identical rows during the years observed in the data was therefore simulated. 

A naive approach would be to assume that each possible row is observed with identical probability. Then, the probability would be:

```{r}
source(pmorethan2identical_naive.R)
```

However we know that a homewin is more probable than the other outcomes and therefore the distribution of rows is biased towards rows with homewins. In this second simulation, we take this into account and we get a significantly higher probability:


```r
source("p_morethan2identical.R")
```
